Wireless Automobile Detection, License Plate Processing, and Data Availability Network Proposal

### 2014-03-07 proposal/proposal.tex
Switched order of sections for better flow.

\subsection{Related Work}
\cite{stillwell2013} describes an implementation of a system to detect automobiles entering and exiting a parking lot using a magnetometer and wireless nodes based on the commercially available Arduino Fio microcontroller platform. This system, uses the ubiquitous IEEE 802.15.4 communications standard to communicate automobile detection data to a central base-station based on the small, commercially available Raspberry Pi Linux computer. The project described in this proposal will augment and extend this project while collaborating closely with Stillwell, to the point of a real world deployment at the Colorado School of Mines.

\section{Proposed Work}
\subsection{Automobile Detection}
Santiago
\subsection{Web Application}
Taylor
\subsection{Raspberry Pi}
Kevin
\subsection{Server Processing}
Brandon
\subsection{Central Basestation}
Everyone

>>>>

\subsection{Related Work}
\cite{stillwell2013} describes an implementation of a system to detect automobiles entering and exiting a parking lot using a magnetometer and wireless nodes based on the commercially available Arduino Fio microcontroller platform. This system uses the ubiquitous IEEE 802.15.4 communications standard to communicate automobile detection data to a central base-station based on the small, commercially available Raspberry Pi Linux computer. The project described in this proposal will augment and extend this project while collaborating closely with Stillwell, to the point of a real world deployment at the Colorado School of Mines.

\section{Proposed Work}
\subsection{Automobile Detection}
Santiago
\subsection{Raspberry Pi Image Collection}
Kevin
\subsection{Central Basestation}
Everyone
\subsection{Server Processing}
Brandon
\subsection{Web Application}
Taylor
